Lineal regression with one variable and one parameter for the cost function

### 2016-07-11 LinearRegression/Documentation/OneParam/OneParam.tex
Fixing orthographic mistakes

    What the algorithm will do is to draw a line as closser as posible to all
    the points in order to get the best aproximation posible to the original
    answers\\

@@

    When the right line is founded we can get an aproximatly answers to
    inputs, that not necesarly where given in first place, allowing to
    get more info from data.\\

    \begin{tikzpicture}
        \begin{axis}[
                      title={Predictions},
                      xlabel=$h(x)$,
                      ylabel=$y$,
                      xmin=0, xmax=5,
                      ymin=0, ymax=10,
                    ]
            \addplot[color=blue]{1.5*x};

@@

    In order to get this line we must define a function that give as the answers
    values, the functionwill be the equation of a line
    \begin{equation}
        h(x) = \theta_0 + \theta_1 x
    \end{equation}

@@

    Lets say that in our problem we are going to have only three points to
    predict. Our function $h(x)$ gave the results $\{5,10,1\}$ and the correct
    results are $\{6,9,3\}$ and we want to cuantificate the error asocciated to
    this two answers.

@@

    To achive this gold we have two posible ways to do it, the first one is to
    add an absolute value to the calculation and the other is to squaring the
    results. The first option is not useful because later we will have to
    calculate a simple derivative to the resulting function and the absolute
    value is not derivable, this let us with the suquare option\\

@@

    The result of this operation is the set $\{1,1,4\}$. Exelent, now we will
    never have a negative number in out resulting set, notice that our
    answers will be much bigger because we are using square of two as our
    method to eliminate the negative numbers, actually this doesn't metter
    because we are lookin for a number that describes the error associated to
    the prediction that we are computing so the range of the number is not too
    important.\\

@@

    Second we are going to define the resulting set as $\{x_1,x_2, ... , x_m\}$
    and the real resulting set as $\{y_1,y_2, ... , y_m\}$. This definition can
    be more concise because the first set is the result of the function $h(x)$,
    so we are going to define it as $h(x_i)$ and the second can be decribed as
    $y_i$.

    Now we will define the substration of each set as follows

@@

    Applying properties of sum

@@

    This is the cuadratic error and will be used as our cost function in terms
    of the parameter $\theta$ to expess the error associated to the prediction
    of the algorithm with respect to the correct output that is given at the
    begin of the problem.

@@

    The next step is define a way to make the error as small as posible,
    to do this we will use a famus algorithm called gradient decend.
    the formula of the algorithm is show bellow

@@

    Before explaining the deeper meaning of this derivative we are going to
    explain in other words what the gradient decend does, imagin that you are
    lost in a jungle that is kind of a valley, and you are trying to find your
    frinds that are in the lowest part of the valley, but you dont know exactly
    in what point of the valley are you, what do you do?\\

@@

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                         title=What you have to imagin as a valley,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=black]{x^2};

@@

    Lets see how can we make our way to the bottom of the valley, the first
    thing to do is find a direction, in order to do this we must know the
    inclination of the side where you are, then start going to the lower place.
    Lets assume that you start in the top left point, when you start going down
    the hill, with a constant step size (this is very important for the
    example), you should notice that you have a big advance with each step
    becouse of the high inclination, but when you are aproaching your friends
    the inclunation is lower and you start to get smaller steps until you get
    your friends and stop walking.

@@

    Now that we have seen the example lets analyze the formula, the fist symbol
    is the $\theta$ that in the example is your position but in the
    formula is the parameter of the cost function, the second symbol is $:=$
    which means that we are updating the value or assigning a new one,
    this make sence because we are trying to get closer to our friends which
    means update the cost function ($J(\theta)$) to the minimum. Then we
    have a second $\theta$ that is your actual possition in the example and
    the actual value of $\theta$ in the formula, followed by a substraction
    that means that we are going to decrement the actual value of $\theta$
    and then assign the new value to $\theta$ trying to get the minimum,
    that means update the value, in the example means walk, then we get an
    $\alpha$ symbol which is a positive number, this represent the step size,
    and is a constant, now we get to the most important part of the formula, the
    derivative ($\frac{d}{d \theta}$).

    Remember that the first thing we do in the example was looked at the
    inclunation of the hill where we are, this in order to know if we should
    move right or left. Now, as you may know a derivative is basicaly the
    slope of a function in a point, this is perfect for us because fit our
    request perfectly. Lets imaging that we start at the right side of the
    valley, so we what to go left, now mathematically the derivative of the
    point situated in the right side of the function is positive because the
    slope is pointing the right, so the term $\frac{d}{d \theta}$ will be a
    positive number, that will be multiplied by a factor ($\alpha$) and then
    substracted to the actual value of $\theta$, just as we want.
    Now lets imaging that we end up in the left side of the valley, in that case
    we want to go right, now mathematically the derivative of a point that is
    situated in the left side of the function will be negative because the
    slope is pointing to the left, this means that the term $\frac{d}{d \theta}$
    will be a negative number, that will be multiplied by the factor ($\alpha$)
    and then added to the actual value of $\theta$ (remember that - * - = +),
    fiting perfectly what we want. now a few ilustrations to show better what we
    are talking about.

@@

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                         title=Gradient decend movement description,
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=-5, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=black]{x^2};

@@

    \begin{tikzpicture}
        \begin{axis}[
                     title={Gradient decend with positive derivative},
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

@@

    \begin{tikzpicture}
        \begin{axis}[
                     title={Gradient decend with negative derivative},
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

@@

    Now to finish the explanation remember the second part of the example, when
    you start to walk, with a constant step size, down the hill you start
    making a big advance because of the inclunation, but when you are getting
    closer to your friends the distance that you move with just one step is
    smaller because the slope of the hill is lower. This is just what we are
    trying to show in the last couple of grafics, notice that when the $\theta$
    is getting closer to the minimum the arrow that represents the movement is
    smaller, this is always going to happen because the inclunation of the hill
    is slower so you move less.\\

@@

    Now the factor of the denominator has no influence on the function so it
    can be tranlated outside of the derivative

@@

    The derivative of the summatory is equal to the derivative of each term and
    then add each result, so we can insert the dirivative into the summary

@@

    Finally we can see the reason why the denominator has a extra factor
    (the 2 that we added at the begining), this is with the objective
    to cancel the 2 in the numerator that result of the derivative. Finaly
    this is the resulting function that we are going to use to minimize the
    error of the algorithm

>>>>

    What the algorithm will do is to draw a line as closser as possible to all
    the points in order to get the best aproximation possible to the original
    answers\\

@@

    When the right line is founded we can get an aproximatly answers to
    inputs, that not necessarily where given in first place, allowing to
    get more info from data.\\

    \begin{tikzpicture}
        \begin{axis}[
                      title={Predictions},
                      xlabel=$x$,
                      ylabel=$h(x)$,
                      xmin=0, xmax=5,
                      ymin=0, ymax=10,
                    ]
            \addplot[color=blue]{1.5*x};

@@

    In order to get this line we must define a function that give us the answers
    values, the function will be the equation of a line
    \begin{equation}
        h(x) = \theta_0 + \theta_1 x
    \end{equation}

@@

    Lets say that in our problem we are going to have only three points to
    predict. Our function $h(x)$ gave the results $\{5,10,1\}$ and the correct
    results are $\{6,9,3\}$ and we want to cuantificate the error associated to
    this two answers.

@@

    To achive this gold we have two possible ways to do it, the first one is to
    add an absolute value to the calculation and the other is to squaring the
    results. The first option is not useful because later we will have to
    calculate a simple derivative to the resulting function and the absolute
    value is not derivable, this let us with the suquare option\\

@@

    The result of this operation is the set $\{1,1,4\}$. Excelent, now we will
    never have a negative number in out resulting set, notice that our
    answers will be much bigger because we are using square of two as our
    method to eliminate the negative numbers, actually this doesn't matter
    because we are looking for a number that describes the error associated to
    the prediction that we are computing so the range of the number is not too
    important.\\

@@

    Second we are going to define the resulting set as $\{x_1,x_2, ... , x_m\}$
    and the real resulting set as $\{y_1,y_2, ... , y_m\}$. This definition can
    be more concise because the first set is the result of the function $h(x)$,
    so we are going to define it as $h(x_i)$ and the second can be described as
    $y_i$.

    Now we will define the subtraction of each set as follows

@@

    Moving the m aside

@@

    This is the cuadratic error and will be used as our cost function in terms
    of the parameter $\theta$ to express the error associated to the prediction
    of the algorithm with respect to the correct output that is given at the
    begin of the problem.

@@

    The next step is define a way to make the error as small as possible,
    to do this we will use a famous algorithm called gradient descend.
    the formula of the algorithm is show bellow

@@

    Before explaining the deeper meaning of this derivative we are going to
    explain in other words what the gradient descend does, imagine that you are
    lost in a jungle that is kind of a valley, and you are trying to find your
    frinds that are in the lowest part of the valley, but you dont know exactly
    in what point you are, what do you do?\\

@@

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                         title=What you have to imagine as a valley,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=black]{x^2};

@@

    Lets see how can we make our way to the bottom of the valley, the first
    thing to do is find a direction, in order to do this we must know the
    inclination of the side where you are, then start going to the lower place.
    Lets assume that you start in the top left point, when you start going down
    the hill, with a constant step size (this is very important for the
    example), you should notice that you have a big advance with each step
    because of the high inclination, but when you are aproaching your friends
    the inclunation is lower and you start to get smaller steps until you get
    your friends and stop walking.

@@

    Now that we have seen the example lets analyze the formula, the first symbol
    is the $\theta$ that in the example is your position but in the
    formula is the parameter of the cost function, the second symbol is $:=$
    which means that we are updating the value or assigning a new one,
    this make sence because we are trying to get closer to our friends, which
    means update the cost function ($J(\theta)$) to the minimum. Then we
    have a second $\theta$ that is your actual possition in the example and
    the actual value of $\theta$ in the formula, followed by a substraction
    that means that we are going to decrement the actual value of $\theta$
    and then assign the new value to $\theta$ trying to get the minimum,
    that means update the value, in the example means walk, then we get an
    $\alpha$ symbol which is a positive number, this represent the step size,
    and is a constant, now we get to the most important part of the formula, the
    derivative ($\frac{d}{d \theta}$).

    Remember that the first thing we do in the example was looked at the
    inclination of the hill where we are, this in order to know if we should
    move right or left. Now, as you may know a derivative is basically the
    slope of a function in a point, this is perfect for us because fit our
    request perfectly. Lets imagine that we start at the right side of the
    valley, so we what to go left, now mathematically the derivative of the
    point situated in the right side of the function is positive because the
    slope is pointing the right, so the term $\frac{d}{d \theta}$ will be a
    positive number, that will be multiplied by a factor ($\alpha$) and then
    substracted to the actual value of $\theta$, just as we want.
    Now lets imagine that we end up in the left side of the valley, in that case
    we want to go right, now mathematically the derivative of a point that is
    situated in the left side of the function will be negative because the
    slope is pointing to the left, this means that the term $\frac{d}{d \theta}$
    will be a negative number, that will be multiplied by the factor ($\alpha$)
    and then added to the actual value of $\theta$ (remember that - * - = +),
    fitting perfectly what we want. now a few ilustrations to show better what we
    are talking about.

@@

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                         title=Gradient descend movement description,
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=-5, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=black]{x^2};

@@

    \begin{tikzpicture}
        \begin{axis}[
                     title={Gradient descend with positive derivative},
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

@@

    \begin{tikzpicture}
        \begin{axis}[
                     title={Gradient descend with negative derivative},
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

@@

    Now to finish the explanation remember the second part of the example, when
    you start to walk, with a constant step size, down the hill you start
    making a big advance because of the inclunation, but when you are getting
    closer to your friends the distance that you move with just one step is
    smaller because the slope of the hill is lower. This is just what we are
    trying to show in the last couple of grafics, notice that when the $\theta$
    is getting closer to the minimum the arrow that represents the movement is
    smaller, this is always going to happen because the inclination of the hill
    is slower so you move less.\\

@@

    Now the factor of the denominator has no influence on the function so it
    can be translated outside of the derivative

@@

    The derivative of the summatory is equal to the derivative of each term and
    then add each result, so we can insert the derivative into the summary

@@

    Finally we can see the reason why the denominator has a extra factor
    (the 2 that we added at the begining), this is with the objective
    to cancel the 2 in the numerator that result of the derivative. Finally
    this is the resulting function that we are going to use to minimize the
    error of the algorithm
